---
title: Átl’ka7tsem/Howe Sound Biosphere Vegetation Analysis
author: Andrew Simon & Antranig Basman
date: December 24, 2022
output: html_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

```{r, echo=FALSE, message=FALSE}
library(here)
root <- "Howe_Sound/story_map_1/"
setwd(here(root))
```

## Introduction

## Howe Sound's vascular plant diversity

Over XXX vascular plant species are known to occur within the Átl’ka7tsem/Howe Sound Biosphere, represented by XX species occurrence records. The flora of the region spans 11 biogeoclimatic units, from lowland dry coastal western hemlock forests and associated woodland communities to high elevation alpine communities.

```{r, echo=FALSE, message=FALSE}
source("scripts/Vascular_plant_map_script.R")
speciesMap
```
### Map 1. Ecological communities

Explore the region's flora by selecting from the following biogeoclimatic units:

Alpine (CMA)
Engelmann spruce subalpine fir communities (ESSFmw)
Mountain hemlock communities (MHmm)
Coastal western hemlock communities (CWHvm,xm,ms,ds,dm)

[Data visualization similar to Xetthecum but summarizing plant diversity by BEC unit with a simplified interface showing just the map, the (selectable) communities, and associated species lists below, including a small image of the species]

## History of collection activities within the region

Scientific documentation of Howe Sound's vascular plant communities dates to 1897, with the collection activities of XXXX. Over the last century and a half, the majority of records stem from collections made during the 19XXs and 2000s, including thousands of observations made by community members through the Howe Sound Biodiversity project over the last decade. [Also include note re: Indigenous knowledge of the regional flora]

# ```{r, echo=FALSE, message=FALSE}
# source("scripts/History_of_collection_activities.R")
# plot
# ```
### Map 2. Historical collection activities

Map cycles through twenty-five decades of search effort, synchronized with a graph showing new species reported over time (choropleth).

## Community science contributions

Through the combined efforts of XX individuals using iNaturalist, our community has documented XXX species, confirming XXX percent of the historically reported vascular plant diversity and adding XX new species reports.

# ```{r, echo=FALSE, message=FALSE}
# source("scripts/Community_science_contributions.R")
# baseMap
# ```
Figure 1: Pie charts / bar plots summarizing how well documented plant families are (e.g., Bio Galiano stats)

Select each plant family to track our progress documenting the regional flora. Unconfirmed historical reports are in green; confirmed historical reports in orange; and new records in blue.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
